Adaptive broadcast tree for multicores

### 2013-05-06 paper.tex
Binary tree for outer network

\begin{description}
\item[synchrony] Parts of a multicore machine are synchronous. Hence,
  one characteristic of a node is an identifier for the synchrony
  cluster of a node.
\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
\end{description}

@@

@@

\begin{description}
\item[breakdown] (quantitative) of message send cost:
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node). Our model is currently limited to only the
  breakdown of the cost for sending messages.
\item[latency] (quantitative) between each pair of nodes (per-edge)
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): 
  multicore interconnect networks often are
\end{description}

>>>>

\begin{description}
\item[NUMA affinity] A list of cores on the same NUMA node
\item[synchrony] Parts of a multicore machine are synchronous. Hence,
  one characteristic of a node is an identifier for the synchrony
  cluster of a node.
\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
\end{description}

@@

%-------------------------------------------------
\subsection{NUMA characteristics}
\label{sec:model_numa_nodes}

The cost of sending a message in a multicore machines does not so much
depend on the distance on the interconnect networks as on the number
of hops on such a path. Propagation on the wire is essentially for
free due to short distances between cores.

On a multi-hop path, however, packages traversing the interconnect
need to be buffered. This is expensive. Depending on the machine,
some routing is executed on every intermediate route, which increases
the latency further.

\begin{description}
\item[hop count] Number of hops to every other NUMA node.
\item[hop count histogram] For every NUMA node, we want to know how
  many other NUMA nodes can be reached with $n$ hops. This tells us
  something about how well such nodes are connected to other NUMA
  nodes. The intuition is that it makes sense to send a message to a
  well connected NUMA node early in time, to ``spread'' out a message
  as quickly as possible.
\end{description}

@@

\begin{description}
\item[breakdown] (quantitative) of message send cost:
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node). Our model is currently limited to only the
  breakdown of the cost for sending messages. Maybe we do not strictly
  need to know about propagation time, as it is negligible independent
  of were messages are sent. Relevant seems to be the number of hops
  rather than the latency expressed in a concrete time.
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): 
  multicore interconnect networks often are
\end{description}
